\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-09 paper.tex
Placeholders
Chapters and sections placeholders
Updates

%\usepackage{qtree}
%\usepackage{tikz}
%\usepackage{tikz-qtree}

%\usepackage[]{algorithm2e}

@@

\title{
\vspace{80pt}\\
\LARGE \bfseries SKEDGE
\\\vspace{10pt}\Large Smarter course scheduling for our\\University of Rochester
}

\author{
	Dan Hassin\\
    \vspace{5pt}\\
    Supervised by Professor Philip Guo\\
    \vspace{5pt}\\
    Department of Computer Science\\
    University of Rochester\\
    Rochester, New York\\
}

\date{April 12, 2016\\
    \vspace{150pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    honors bachelor of science\\
}

@@

@@

% Direct search for specific course
% Discovery, browsing, exploring
% behavioral patterns

% STAT: Find major of users, find how many non-major courses they found

@@

@@

\tableofcontents

\include{01-introduction}

\include{04-conclusion}

@@

	\bibitem{esprima} Ariya Hidayat {\em Esprima}
		\\\url{http://esprima.org/}

@@

	\bibitem{hosa} Frank Pfenning, Conal Elliott
		{\em Higher-Order Abstract Syntax.}
		ACM SIGPLAN Notices. Vol. 23. No. 7. ACM, 1988.
		\\\url{http://www.cs.cmu.edu/~fp/papers/pldi88.pdf}

	\bibitem{escodegen} Yusuke Suzuki {\em Escodegen}
		\\\url{https://github.com/Constellation/escodegen}

	\bibitem{parser api} Mozilla Developer Network {\em SpiderMonkey Parser API}
		\\\url{https://developer.mozilla.org/en-US/docs/SpiderMonkey/Parser_API}

@@

>>>>

@@

\title{
\vspace{60pt}\\
\huge \bfseries SKEDGE
\\
\vspace{10pt}
\Large
Smarter course scheduling for our\\
University of Rochester
}

\author{
	Dan Hassin\\
    \vspace{5pt}\\
    Supervised by\\
    Professor Philip Guo\\
    \vspace{2pt}\\
    Department of Computer Science\\
    University of Rochester\\
    Rochester, New York\\
}

\date{April 12, 2016\\
    \vspace{150pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    \emph{honors bachelor of science}\\
}

@@

%%%%%%%%%%%

\onehalfspacing

\pagenumbering{gobble}
\setcounter{tocdepth}{1}
\tableofcontents

\listoftables

\listoffigures

%%%%%%%%%%%%%%%%%%

@@

\addcontentsline{toc}{chapter}{Abstract}

@@

\thispagestyle{plain}
\pagenumbering{roman}

@@

%%%%%%%%%%%%%%%

\pagenumbering{arabic}

\include{introduction}
\clearpage

\include{01-grievances}
\clearpage

\include{02-tech}
\clearpage

\include{03-analytics}
\clearpage

\include{04-future}
\clearpage

\include{conclusion}
\clearpage

@@

@@

@@

\addcontentsline{toc}{chapter}{Bibliography}
